Hypertension and microbiome

### 2019-09-02 articletwo.Rmd
Deseq2

```{r deseq2, eval = FALSE}
pseq.genus.core.deseq <- pseq.genus %>% core(detection = 0.0001, prevalence = 0.01)

@@

#dds = DESeq(dds.data, test="Wald", fitType="parametric")
#resultsNames(dds)
#res = results(dds)

@@

res <- results(dds)
df <- as.data.frame(res)
df$taxon <- rownames(df)
  #df <- df %>% arrange(pvalue) # TODO

@@

>>>>

```{r deseq2}
pseq.genus.core.deseq <- pseq.genus %>% core(detection = 0.0001, prevalence = 0.01)

@@

@@

res <- results(dds)
df <- as.data.frame(res)
df$taxon <- rownames(df)

@@

df %>% kable
```
